### 2020-06-26 Documents/ESA/sections/ResearchSummary.tex
Updated ESA
Restructuring of ESA

	\begin{subequations}
	\label{eqn::EOM}
		\begin{equation}
			\frac{\dot{x}(t)}{x(t)} = \alpha \tau (\sum_{j} a_{ij} y_j - \sum_{i j} x_i a_{ij} y_j)
			+ \alpha \sum_j x_j ln(\frac{x_j}{x_i}) 
		\end{equation}
		\begin{equation}
			\frac{\dot{y}(t)}{y(t)} = \alpha \tau (\sum_{j} b_{ij} x_j - \sum_{i j} y_i b_{ij} x_j)
			+ \alpha \sum_j y_j ln(\frac{y_j}{y_i}).
		\end{equation}
	\end{subequations}

@@

	\subsection{Rescaling of Variables} % (fold)
	\label{sub:rescaling_of_variables}

@@

	\begin{subequations}
	\label{eqn::scaledEOM}
		\begin{equation}
			\frac{\dot{\tilde{x_i}}(t)}{\tilde{x_i}(t)} = \alpha \tilde{\tau} \sum_{j} \tilde{a_
			{ij}} 
			\tilde{y_j} -
			\tilde{\alpha} \tau \frac{1}{\sqrt{N}} \sum_{i j} \tilde{x_i} \tilde{a_{ij}} \tilde{y_j}
			+ \tilde{\alpha} \sum_j \tilde{x_j} ln(\frac{\tilde{x_j}}{\tilde{x_i}}) 
		\end{equation}
		\begin{equation}
			\frac{\dot{\tilde{y_i}}(t)}{\tilde{y_i}(t)} = \alpha \tilde{\tau} \sum_{j} \tilde{b_
			{ij}} 
			\tilde{x_j} -
			\tilde{\alpha} \tau \frac{1}{\sqrt{N}} \sum_{i j} \tilde{y_i} \tilde{b_{ij}} \tilde{x_j}
			+ \tilde{\alpha} \sum_j \tilde{y_j} ln(\frac{\tilde{y_j}}{\tilde{y_i}}).
		\end{equation}
	\end{subequations}

@@

	\subsection{Generating Functional} % (fold)
	\label{sub:generating_functional}

	The generating functional allows us to take a path integral over all possible realisations of
	learning \cite{SpinGlassTheory}. This is given as:

@@

	where the equations of motion are the Lagrange equations of motion given in (
	\ref{eqn::scaledEOM}) andSince
	the fields $\Vec{\psi_i(t)}$ and $\Vec{\phi_i(t)}$ will be set to zero at the end of the
	calculation. $\delta$ denotes the Dirac delta function. We write this in its Fourier
	representation, which yields

	\begin{equation}
		\begin{split}
	\label{eqn::generatingfunctional}
		Z(\Vec{\psi}, \Vec{\phi}) = \int D[\Vec{x}, \Vec{\hat{x}}, \Vec{y}, \Vec{\hat{y}}] exp(i \sum_i \int dt[\hat{x}_i
		(\frac{\dot{x_i}(t)}{x_i(t)} - \alpha \tilde{\tau} \sum_{j} a_
			{ij} 
			y_j +
			\tilde{\alpha} \tau \frac{1}{\sqrt{N}} \sum_{i j} x_i a_{ij} y_j
			- \tilde{\alpha} \rho_{x, i}(t) + h_{x, i}(t))]) 
			\\
			\times exp(i \sum_i \int dt[\hat{y}_i
		(\frac{\dot{y_i}(t)}{y_i(t)} - \alpha \tilde{\tau} \sum_{j} b_
			{ij} 
			x_j +
			\tilde{\alpha} \tau \frac{1}{\sqrt{N}} \sum_{i j} y_i b_{ij} x_j
			- \tilde{\alpha} \rho_{y, i}(t)+ h_{y, i}(t))])\\
			\times exp(i \sum_i
		\int dt[x_i(t) \psi_i(t) + y_i(t) \phi_i(t))]),
	\end{split}
	\end{equation}

@@

	\begin{equation}
	\begin{split}
	\label{eqn::moveddisorder}
		Z(\Vec{\psi}, \Vec{\phi}) = \int D[\Vec{x}, \Vec{\hat{x}}, \Vec{y}, \Vec{\hat{y}}] exp(i
		\sum_i \int dt[\hat{x}_i
		(\frac{\dot{x_i}(t)}{x_i(t)}
			- \tilde{\alpha} \rho_{x, i}(t)+ h_{x, i}(t))]) 
			\\
			\times exp(i \sum_i \int dt[\hat{y}_i
		(\frac{\dot{y_i}(t)}{y_i(t)} 
			- \tilde{\alpha} \rho_{y, i}(t) + h_{y, i}(t))])\\
			\times exp(i \sum_i
		\int dt[x_i(t) \psi_i(t) + y_i(t) \phi_i(t))])\\
		\times exp(i \sum_i \int dt[- \hat{x}_i \alpha \tilde{\tau} \sum_{j} a_
			{ij} 
			y_j +
			\hat{x}_i \tilde{\alpha} \tau \frac{1}{\sqrt{N}} \sum_{i j} x_i a_{ij} y_j - \hat{y}_i
			\alpha 
			\tilde{\tau} \sum_{j} b_
			{ij} 
			x_j +
			\hat{y}_i \tilde{\alpha} \tau \frac{1}{\sqrt{N}} \sum_{i j} y_i b_{ij} x_j]).
	\end{split}
	\end{equation}
	The only difference between (\ref{eqn::generatingfunctional}) and (\ref{eqn::moveddisorder}) is
	that we moved the term containing the quenched disorder into a separate exponential. Since our
	aim is to take an average over all possible realisations of this disorder, we will only need to
	focus on the last exponential which we rewrite as

@@

	\begin{equation}
	\label{eqn::expectationIdentity}
		\int dz [e^{-A_2(z) + \Vec{b} \cdot \Vec{z}}] = (2 \pi)^{k/2} (det(A))^{-1/2} e^{\omega(b)},
	\end{equation}

@@

	\subsubsection{Expectation of $Q_1$} % (fold)
	\label{ssub:expectation_of_Q1}

@@

	Applying identity (\ref{eqn::expectationIdentity}) gives:

@@

	\subsubsection{Expectation of $Q_2$} % (fold)
	\label{ssub:expectation_of_Q2}

@@

Since this contains all of the information of the learning evolution, we consider $\Omega$ as an
effective generating functional (and in fact we see that it has a similar structure to (
\ref{sub:generating_functional}), without the existence of the fields $\psi, \phi$). In particular
we recognise this as the generating functional of the 'effective dynamics' given as

@@

\section{Stability Analysis} % (fold)
\label{sec:stability_analysis}

We are now in a position to take the effective dynamics, which describes the evolution of the
learning dynamics after averaging over all possible realisations of the payoff elements, and
determine the stability of the system at fixed points. We will follow the procedure laid out by
Opper et al \cite{Opper}. First, we rewrite $x(t)$, $y(t)$ as perturbations about their fixed
points. We will then analyse the stability of these fixed points.

@@

\begin{equation} 
	\label{eqn::Linearisation}
	\begin{split}
	\frac{d}{dt} \hat{x}(t) = (x^* + \hat{x}(t))\left[ \Gamma \alpha^2 \tilde{\tau}^2 x^* \int G_y(t - t') dt' + \tilde{\alpha} \rho_x^* + \alpha \tilde{\tau} \eta_x^* + \tilde{\alpha} \tau \eta_x^* \eta_y^* + \Gamma \tilde{\alpha} \tau \mu_x \right] \\
	+ x^* \left[ \Gamma \alpha^2 \tilde{\tau}^2 \int G_y(t - t') \hat{x}(t') dt' + \alpha \tilde{\tau} \hat{\nu}_x(t) + \tilde{\alpha} \tau \eta_x^* \hat{\nu}_y(t) + \tilde{\alpha} \tau \eta_y^* \hat{\nu}_x(t) + \sqrt{\Gamma} \tilde{\alpha} \tau \hat{\delta}_x(t) + \xi(t) \right]\\
	\frac{d}{dt} \hat{y}(t) = (y^* + \hat{y}(t))\left[ \Gamma \alpha^2 \tilde{\tau}^2 x^* \int G_x(t - t') dt' + \tilde{\alpha} \rho_y^* + \alpha \tilde{\tau} \eta_y^* + \tilde{\alpha} \tau \eta_x^* \eta_y^* + \Gamma \tilde{\alpha} \tau \mu_y \right] \\
	+ y^* \left[ \Gamma \alpha^2 \tilde{\tau}^2 \int G_x(t - t') \hat{y}(t') dt' + \alpha \tilde{\tau} \hat{\nu}_y(t) + \tilde{\alpha} \tau \eta_x^* \hat{\nu}_y(t) + \tilde{\alpha} \tau \eta_y^* \hat{\nu}_x(t) + \sqrt{\Gamma} \tilde{\alpha} \tau \hat{\delta}_y(t) + \zeta(t) \right].\\
	\end{split}
\end{equation}

@@

We continue to follow the method of Opper et al. by taking the Fourier transform of (\ref{eqn::Linearisation}). For both agents, the first term in square brackets is constant with respect to time and so will not affect the long term behaviour of the system. We can, therefore, ignore this and focus on the second term. For the sake of brevity, we will only write the equations for Agent 1 (i.e. for $x$), though the equations for y can be equivalently obtained. Taking the Fourier transform yields

@@

\begin{equation} \label{eqn::Transformed}
	\left<[|\mathcal{X}(\omega)|^2 \right> = \left< | \Gamma \alpha \tilde{\tau} \mathcal{V}_x(\omega) + \tilde{\alpha} \tau \eta^*_x \mathcal{V}_y(\omega) + \tilde{\alpha} \tau \eta^*_y \mathcal{V}_x(\omega) + \sqrt{\Gamma} \tilde{\alpha} \tau \Delta(\omega) + \Xi(\omega) |^2 \right> \frac{1}{\left< |\mathcal{A}(\omega, x^*) |^2 \right>}, 
\end{equation}

@@

\section{Numerical Simulations} % (fold)
\label{sec:numerical_simulations}

\begin{figure}[h]
	\centering
	\begin{subfigure}[b]{0.45 \textwidth}
	\centering
	\includegraphics[width = 0.7 \textwidth]{Figures/Run1.png}
	\caption{$\alpha = 0.1$}
	\end{subfigure}
	\begin{subfigure}[b]{0.45 \textwidth}
	\centering
	\includegraphics[width = 0.7 \textwidth]{Figures/Run2.png}
	\caption{$\alpha = 0.1$}
	\end{subfigure}
	%
	\begin{subfigure}[b]{0.45 \textwidth}
	\centering
	\includegraphics[width = 0.7 \textwidth]{Figures/Alpha_2.png}
	\caption{$\alpha = 0.2$}
	\end{subfigure}
	\begin{subfigure}[b]{0.45 \textwidth}
	\centering
	\includegraphics[width = 0.7 \textwidth]{Figures/Alpha_2_Run_2.png}
	\caption{$\alpha = 0.1$}
	\end{subfigure}
	%
	\begin{subfigure}[b]{0.45 \textwidth}
	\centering
	\includegraphics[width = 0.7 \textwidth]{Figures/tau_005.png}
	\caption{$\tau = 0.0$}
	\end{subfigure}
	\begin{subfigure}[b]{0.45 \textwidth}
	\centering
	\includegraphics[width = 0.7 \textwidth]{Figures/tau_015.png}
	\caption{$\tau = 0.15$}
	\end{subfigure}

	\caption{$\alpha = 0.1$, $\gamma = 0.1$, $\tau \in [0.1, 10]$, $\Gamma \in [-1, 1]$. Each
	simulation is run for 1e5 iterations and tested for convergence. The game is said to have
	converged based on a tolerance of 1\% difference between action probabilities. For each
	combination of $\tau$, $\Gamma$ the game is played 5 times, each with random payoff matrices
	and initial conditions. The average number of converged games (giving an indication of
	probability of convergence) is shown in each cell of the heatmap. \label{fig::Toys}}
\end{figure}

To generate the numerical simulations in Figure \ref{fig::Toys} we used the following procedure.

\begin{enumerate}
	\item Fix the parameters $\alpha$ and $\gamma$. The latter is held fixed at $0.1$ since
	it does not affect the long term behaviour of the system (it does not appear in (
	\ref{eqn::EOM})).
	\item We initialise values of $\Gamma$ and $\tau$. These will be the variables which we sweep
	over.
	\item Generate payoff matrices for both agents by sampling from a multi-variate Gaussian 
	(variables are the payoff elements) with covariance parameterised by $\Gamma$.
	\item Iniitialise the agents with random initial conditions (i.e. random action probabilities).
	\item Allow the agents to learn over a maximum of $1 \times 10^5$ iterations.
	\item Every 100 iterations, check to see if the action probabilities have changed significantly.
	If not (i.e. the change over the last 100 iterations is less than 1\%) the learning is
	considered to have converged.
	\item This process is repeated 5 times with random payoff matrices generated based on the value
	of $\Gamma$. The probability of convergence is then recorded as $\frac{\text{number of times
	converged}}{5}$.
	\item The values of $\tau$ and $\Gamma$ are then modified and the process is repeated. The
	heatmap shows the probability of convergence for all values of $\tau$ and $\Gamma$ which are
	tested.
\end{enumerate}

>>>>

	\begin{subequations}
	\label{eqn::appEOM}
		\begin{equation}
			\frac{\dot{x}(t)}{x(t)} = \alpha \tau (\sum_{j} a_{ij} y_j - \sum_{i j} x_i a_{ij} y_j)
			+ \alpha \sum_j x_j ln(\frac{x_j}{x_i}) 
		\end{equation}
		\begin{equation}
			\frac{\dot{y}(t)}{y(t)} = \alpha \tau (\sum_{j} b_{ij} x_j - \sum_{i j} y_i b_{ij} x_j)
			+ \alpha \sum_j y_j ln(\frac{y_j}{y_i}).
		\end{equation}
	\end{subequations}

@@

	\section{Rescaling of Variables} % (fold)
	\label{sub:apprescaling_of_variables}

@@

	\begin{subequations}
	\label{eqn::appscaledEOM}
		\begin{equation}
			\frac{\dot{\tilde{x_i}}(t)}{\tilde{x_i}(t)} = \alpha \tilde{\tau} \sum_{j} \tilde{a_
			{ij}} 
			\tilde{y_j} -
			\tilde{\alpha} \tau \frac{1}{\sqrt{N}} \sum_{i j} \tilde{x_i} \tilde{a_{ij}} \tilde{y_j}
			+ \tilde{\alpha} \sum_j \tilde{x_j} ln(\frac{\tilde{x_j}}{\tilde{x_i}}) 
		\end{equation}
		\begin{equation}
			\frac{\dot{\tilde{y_i}}(t)}{\tilde{y_i}(t)} = \alpha \tilde{\tau} \sum_{j} \tilde{b_
			{ij}} 
			\tilde{x_j} -
			\tilde{\alpha} \tau \frac{1}{\sqrt{N}} \sum_{i j} \tilde{y_i} \tilde{b_{ij}} \tilde{x_j}
			+ \tilde{\alpha} \sum_j \tilde{y_j} ln(\frac{\tilde{y_j}}{\tilde{y_i}}).
		\end{equation}
	\end{subequations}

@@

	\section{Generating Functional} % (fold)
	\label{sub:appgenerating_functional}

	The generating functional allows us to take a path integral over all possible realisations of
	learning \cite{Mezard1986}. This is given as:

@@

	where the equations of motion are the Lagrange equations of motion given in (
	\ref{eqn::appscaledEOM}) and
	the fields $\Vec{\psi_i(t)}$ and $\Vec{\phi_i(t)}$ will be set to zero at the end of the
	calculation. $\delta$ denotes the Dirac delta function. We write this in its Fourier
	representation, which yields

	\begin{equation}
		\begin{split}
	\label{eqn::appgeneratingfunctional}
		Z(\Vec{\psi}, \Vec{\phi}) = \int D[\Vec{x}, \Vec{\hat{x}}, \Vec{y}, \Vec{\hat{y}}] exp(i \sum_i \int dt[\hat{x}_i
		(\frac{\dot{x_i}(t)}{x_i(t)} - \alpha \tilde{\tau} \sum_{j} a_
			{ij} 
			y_j +
			\tilde{\alpha} \tau \frac{1}{\sqrt{N}} \sum_{i j} x_i a_{ij} y_j
			- \tilde{\alpha} \rho_{x, i}(t) + h_{x, i}(t))]) 
			\\
			\times exp(i \sum_i \int dt[\hat{y}_i
		(\frac{\dot{y_i}(t)}{y_i(t)} - \alpha \tilde{\tau} \sum_{j} b_
			{ij} 
			x_j +
			\tilde{\alpha} \tau \frac{1}{\sqrt{N}} \sum_{i j} y_i b_{ij} x_j
			- \tilde{\alpha} \rho_{y, i}(t)+ h_{y, i}(t))])\\
			\times exp(i \sum_i
		\int dt[x_i(t) \psi_i(t) + y_i(t) \phi_i(t))]),
	\end{split}
	\end{equation}

@@

	\begin{equation}
	\begin{split}
	\label{eqn::appmoveddisorder}
		Z(\Vec{\psi}, \Vec{\phi}) = \int D[\Vec{x}, \Vec{\hat{x}}, \Vec{y}, \Vec{\hat{y}}] exp(i
		\sum_i \int dt[\hat{x}_i
		(\frac{\dot{x_i}(t)}{x_i(t)}
			- \tilde{\alpha} \rho_{x, i}(t)+ h_{x, i}(t))]) 
			\\
			\times exp(i \sum_i \int dt[\hat{y}_i
		(\frac{\dot{y_i}(t)}{y_i(t)} 
			- \tilde{\alpha} \rho_{y, i}(t) + h_{y, i}(t))])\\
			\times exp(i \sum_i
		\int dt[x_i(t) \psi_i(t) + y_i(t) \phi_i(t))])\\
		\times exp(i \sum_i \int dt[- \hat{x}_i \alpha \tilde{\tau} \sum_{j} a_
			{ij} 
			y_j +
			\hat{x}_i \tilde{\alpha} \tau \frac{1}{\sqrt{N}} \sum_{i j} x_i a_{ij} y_j - \hat{y}_i
			\alpha 
			\tilde{\tau} \sum_{j} b_
			{ij} 
			x_j +
			\hat{y}_i \tilde{\alpha} \tau \frac{1}{\sqrt{N}} \sum_{i j} y_i b_{ij} x_j]).
	\end{split}
	\end{equation}
	The only difference between (\ref{eqn::appgeneratingfunctional}) and (\ref{eqn::appmoveddisorder}) is
	that we moved the term containing the quenched disorder into a separate exponential. Since our
	aim is to take an average over all possible realisations of this disorder, we will only need to
	focus on the last exponential which we rewrite as

@@

	\begin{equation}
	\label{eqn::appexpectationIdentity}
		\int dz [e^{-A_2(z) + \Vec{b} \cdot \Vec{z}}] = (2 \pi)^{k/2} (det(A))^{-1/2} e^{\omega(b)},
	\end{equation}

@@

	\subsection{Expectation of $Q_1$} % (fold)
	\label{ssub:appexpectation_of_Q1}

@@

	Applying identity (\ref{eqn::appexpectationIdentity}) gives:

@@

	\subsection{Expectation of $Q_2$} % (fold)
	\label{ssub:appexpectation_of_Q2}

@@

Since this contains all of the information of the learning evolution, we consider $\Omega$ as an
effective generating functional (and in fact we see that it has a similar structure to (
\ref{sub:appgenerating_functional}), without the existence of the fields $\psi, \phi$). In particular
we recognise this as the generating functional of the 'effective dynamics' given as

@@

\section{Stability Analysis} % (fold)
\label{sec:appstability_analysis}

We are now in a position to take the effective dynamics, which describes the evolution of the
learning dynamics after averaging over all possible realisations of the payoff elements, and
determine the stability of the system at fixed points. We will follow the procedure laid out by
Opper et al \cite{Opper1992}. First, we rewrite $x(t)$, $y(t)$ as perturbations about their fixed
points. We will then analyse the stability of these fixed points.

@@

\begin{equation} 
	\label{eqn::appLinearisation}
	\begin{split}
	\frac{d}{dt} \hat{x}(t) = (x^* + \hat{x}(t))\left[ \Gamma \alpha^2 \tilde{\tau}^2 x^* \int G_y(t - t') dt' + \tilde{\alpha} \rho_x^* + \alpha \tilde{\tau} \eta_x^* + \tilde{\alpha} \tau \eta_x^* \eta_y^* + \Gamma \tilde{\alpha} \tau \mu_x \right] \\
	+ x^* \left[ \Gamma \alpha^2 \tilde{\tau}^2 \int G_y(t - t') \hat{x}(t') dt' + \alpha \tilde{\tau} \hat{\nu}_x(t) + \tilde{\alpha} \tau \eta_x^* \hat{\nu}_y(t) + \tilde{\alpha} \tau \eta_y^* \hat{\nu}_x(t) + \sqrt{\Gamma} \tilde{\alpha} \tau \hat{\delta}_x(t) + \xi(t) \right]\\
	\frac{d}{dt} \hat{y}(t) = (y^* + \hat{y}(t))\left[ \Gamma \alpha^2 \tilde{\tau}^2 x^* \int G_x(t - t') dt' + \tilde{\alpha} \rho_y^* + \alpha \tilde{\tau} \eta_y^* + \tilde{\alpha} \tau \eta_x^* \eta_y^* + \Gamma \tilde{\alpha} \tau \mu_y \right] \\
	+ y^* \left[ \Gamma \alpha^2 \tilde{\tau}^2 \int G_x(t - t') \hat{y}(t') dt' + \alpha \tilde{\tau} \hat{\nu}_y(t) + \tilde{\alpha} \tau \eta_x^* \hat{\nu}_y(t) + \tilde{\alpha} \tau \eta_y^* \hat{\nu}_x(t) + \sqrt{\Gamma} \tilde{\alpha} \tau \hat{\delta}_y(t) + \zeta(t) \right].\\
	\end{split}
\end{equation}

@@

We continue to follow the method of Opper et al. by taking the Fourier transform of (\ref{eqn::appLinearisation}). For both agents, the first term in square brackets is constant with respect to time and so will not affect the long term behaviour of the system. We can, therefore, ignore this and focus on the second term. For the sake of brevity, we will only write the equations for Agent 1 (i.e. for $x$), though the equations for y can be equivalently obtained. Taking the Fourier transform yields

@@

\begin{equation} \label{eqn::appTransformed}
	\left<[|\mathcal{X}(\omega)|^2 \right> = \left< | \Gamma \alpha \tilde{\tau} \mathcal{V}_x(\omega) + \tilde{\alpha} \tau \eta^*_x \mathcal{V}_y(\omega) + \tilde{\alpha} \tau \eta^*_y \mathcal{V}_x(\omega) + \sqrt{\Gamma} \tilde{\alpha} \tau \Delta(\omega) + \Xi(\omega) |^2 \right> \frac{1}{\left< |\mathcal{A}(\omega, x^*) |^2 \right>}, 
\end{equation}

@@

\section{Numerical Simulations} % (fold)
\label{sec:appnumerical_simulations}

\begin{figure}[h]
	\centering
	\begin{subfigure}[b]{0.45 \textwidth}
	\centering
	\includegraphics[width = 0.7 \textwidth]{Figures/Run1.png}
	\caption{$\alpha = 0.1$}
	\end{subfigure}
	\begin{subfigure}[b]{0.45 \textwidth}
	\centering
	\includegraphics[width = 0.7 \textwidth]{Figures/Run2.png}
	\caption{$\alpha = 0.1$}
	\end{subfigure}
	%
	\begin{subfigure}[b]{0.45 \textwidth}
	\centering
	\includegraphics[width = 0.7 \textwidth]{Figures/Alpha_2.png}
	\caption{$\alpha = 0.2$}
	\end{subfigure}
	\begin{subfigure}[b]{0.45 \textwidth}
	\centering
	\includegraphics[width = 0.7 \textwidth]{Figures/Alpha_2_Run_2.png}
	\caption{$\alpha = 0.1$}
	\end{subfigure}
	%
	\begin{subfigure}[b]{0.45 \textwidth}
	\centering
	\includegraphics[width = 0.7 \textwidth]{Figures/AlphaRun_tau_005.png}
	\caption{$\tau = 0.05$}
	\end{subfigure}
	\begin{subfigure}[b]{0.45 \textwidth}
	\centering
	\includegraphics[width = 0.7 \textwidth]{Figures/tau_015.png}
	\caption{$\tau = 0.15$}
	\end{subfigure}

	\caption{$\alpha = 0.1$, $\gamma = 0.1$, $\tau \in [0.1, 10]$, $\Gamma \in [-1, 1]$. Each
	simulation is run for 1e5 iterations and tested for convergence. The game is said to have
	converged based on a tolerance of 1\% difference between action probabilities. For each
	combination of $\tau$, $\Gamma$ the game is played 5 times, each with random payoff matrices
	and initial conditions. The average number of converged games (giving an indication of
	probability of convergence) is shown in each cell of the heatmap. \label{fig::appToys}}
\end{figure}

To generate the numerical simulations in Figure \ref{fig::appToys} we used the following procedure.

\begin{enumerate}
	\item Fix the parameters $\alpha$ and $\gamma$. The latter is held fixed at $0.1$ since
	it does not affect the long term behaviour of the system (it does not appear in (
	\ref{eqn::appEOM})).
	\item We initialise values of $\Gamma$ and $\tau$. These will be the variables which we sweep
	over.
	\item Generate payoff matrices for both agents by sampling from a multi-variate Gaussian 
	(variables are the payoff elements) with covariance parameterised by $\Gamma$.
	\item Iniitialise the agents with random initial conditions (i.e. random action probabilities).
	\item Allow the agents to learn over a maximum of $1 \times 10^5$ iterations.
	\item Every 100 iterations, check to see if the action probabilities have changed significantly.
	If not (i.e. the change over the last 100 iterations is less than 1\%) the learning is
	considered to have converged.
	\item This process is repeated 5 times with random payoff matrices generated based on the value
	of $\Gamma$. The probability of convergence is then recorded as $\frac{\text{number of times
	converged}}{5}$.
	\item The values of $\tau$ and $\Gamma$ are then modified and the process is repeated. The
	heatmap shows the probability of convergence for all values of $\tau$ and $\Gamma$ which are
	tested.
\end{enumerate}
